miniKanren with fair search strategies

### 2019-05-20 Paper/paper.tex
improve typesetting

\lstset{
  language=Scheme,
  basicstyle=\ttfamily,
  morekeywords={run,conde,run*,defrel,==,fresh},
  alsodigit={!\$\%&*+-./:<=>?@^_~},
  morecomment=[l]{;,\#{}lang},
  mathescape=true
}
%% scheme-list .

@@

\begin{center}
	\begin{tabular}{c}
		\lstinputlisting{Figures/repeato-disj-DFSf.rkt}
	\end{tabular}
\end{center}
\begin{center}
\begin{tabular}{c}
	\lstinputlisting{Figures/repeato-disj-BFS.rkt}
\end{tabular}
\end{center}

@@

\begin{center}
	\begin{tabular}{c}
		\lstinputlisting{Figures/repeato-conj-DFSi.rkt}
	\end{tabular}
\end{center}

\begin{center}
	\begin{tabular}{c}
		\lstinputlisting{Figures/repeato-conj-DFSf.rkt}
	\end{tabular}
\end{center}

\begin{center}
	\begin{tabular}{c}
		\lstinputlisting{Figures/repeato-conj-DFSbi.rkt}
	\end{tabular}
\end{center}

>>>>

\lstset{
  language=Scheme,
  basicstyle=\ttfamily,
  morekeywords={run,conde,run*,defrel,==,fresh},
  alsodigit={!\$\%&*+-./:<=>?@^_~},
  morecomment=[l]{;,\#{}lang},
  mathescape=true,
  literate={-inf}{{$^\infty$}}1 {/fair}{{$_{fair}$}}3
  		   {→}{{$\rightarrow$}}1
  		   {×}{{$\times$}}1
  		   {conde}{{cond$^e$}}4
  		   {repeato}{{repeat$^o$}}6
}
%% scheme-list .

@@

\begin{center}
	\begin{tabular}{l|r}
		\lstinputlisting{Figures/repeato-disj-DFSf.rkt} &
		\lstinputlisting{Figures/repeato-disj-BFS.rkt}
	\end{tabular}
\end{center}

@@

\begin{center}
\begin{tabular}{l|c|r}
    \lstinputlisting{Figures/repeato-conj-DFSi.rkt} &
    \lstinputlisting{Figures/repeato-conj-DFSf.rkt} &
    \lstinputlisting{Figures/repeato-conj-DFSbi.rkt} \\
\end{tabular}
\end{center}
